Black-hole ringdown as a probe of higher-curvature gravity theories

### 2022-04-19 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: commiting local changes to be able to pull
hs" fixed caption in the appendix plot

\begin{figure*}[t]
\includegraphics[width=0.9\textwidth]{figs/tmp_GW150914_intrinsic_params.pdf}
\caption{(Color online).~Corner plot showing that the inferred final spin $\chi_f$,
detector-frame remnant mass $M_f$ for GW150914, using the same waveform model,
but without (purple contours) and with the non-GR parameters different from zero (blue contours, for
dCS gravity and $N_{\rm max}=0$). The contours represent 90\% credible levels.
%
We see that the introduction of the non-GR parameters does not bias the
inference on the source parameters.
%
We observe the same qualitative behavior in the posteriors for the other modified gravity theories
studied in the main text.
}
\label{fig:corner_plot_all}
\end{figure*}

@@

In this Appendix, we show how we fixed the coefficients in the ParSpec using
QNM calculations found in the literature for the theories described in
Sec.~\ref{sec:review_theories}.

>>>>

\begin{figure*}[t]
\includegraphics[width=0.9\textwidth]{figs/tmp_GW150914_intrinsic_params.pdf}
\caption{(Color online).~Corner plot showing that the inferred source binary parameters for GW150914,
using the same waveform model \pSEOB, but with (purple contours) and without setting the non-GR parameters different
from zero (blue contours), having as an illustrative example dCS gravity and $N_{\rm max}=0$.
%
All contours correspond to 90\% credible levels.
%
We see that the introduction of the non-GR parameters does not bias the
inference of the source parameters.
%
We found the same qualitative behavior in the posteriors distributions of the
source binary parameters for the other modified gravity theories studied in the
main text.
%
The same conclusions apply for the other GW event studied here, GW200129.
}
\label{fig:corner_plot_all}
\end{figure*}

@@

In this Appendix, we show how we determined the coefficients in the ParSpec
using QNM calculations found in the literature for the theories described in
Sec.~\ref{sec:review_theories}.
